Concurrent Programming in Harmony

### 2022-01-15 book/paper.tex
Improved concurrent queue test program

We will start with a test program that tries concurrent combinations
of various queue operations.
\autoref{fig:qtestpar} shows the test program.  It starts
<{NOPS}> threads, and each choose to do either a <{put}>
or a <{get}> operation.  In case of a <{put}> operation,
the thread enqueues its own name (which is provided as an argument
to the thread).  In order to capture the behaviors,
each thread prints what operation it is about to perform,
and afterwards it prints that the operation has
completed (including the return value if any).
This is probably much like you would do if you were trying to find a
bug in a program.

@@

@@

>>>>

We will start with a test program that tries concurrent combinations
of various queue operations.
\autoref{fig:qtestpar} shows the test program.  It starts
<{NOPS}> threads doing either a <{put}>
or a <{get}> operation.  It selects the fraction of <{put}>
over <{get}> operations nondetermistically, although avoiding the
uninteresting case in which there are none of one of them.
In case of a <{put}> operation,
the thread enqueues its own name (which is provided as an argument
to the thread).  In order to capture the behaviors,
each thread prints what operation it is about to perform,
and afterwards it prints that the operation has
completed (including the return value if any).
This is probably much like you would do if you were trying to find a
bug in a program.

@@

\begin{figure}
\begin{code}
<{:input:../code/RWbusy.hny}>
\end{code}
\caption{\harmonylink{code/RWbusy.hny} Busy waiting reader/writer lock}
\label{fig:rwbusy}
\end{figure}

@@

\autoref{fig:rwbusy} illustrates an implementation of a reader/writer lock
that uses active busy waiting.  This is an undesirable solution, as it wastes
CPU cycles.  Harmony complains about this solution.
